### 2014-10-03 LaTeX/RhodiumEmp.tex
updates

To measure economic performance we use annual percent change in logged GDP collected from the World Development Indicators at the World Bank. We choose to focus on year over change in logged GDP because we expect conflicts proximate to major cities to lead to immediate reductions in overall growth. Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average. This allows us to estimate the direct effect of conflict on economic performance in that year. A ten-year average approach would hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.

Our key independent variable on the location of conflicts come from the PRIO Conflict Site Dataset. This dataset contains geo-referenced armed conflict events from 1989 to 2008.\footnote{We only include examine the effect of internal armed conflicts.} In total this dataset provides us with almost 800 geo-referenced conflict-year cases.

A crucial part of our work here involved determining the capital and major city centers for country-years referenced in the PRIO dataset.\footnote{To gather information on capital and major cities we turned to yearly editions of The World Almanac from 1989 to 2008.} Typically, the Alamanacs listed at least three major cities for each country and year from 1989 to 2008. After we had gathered a yearly list of major cities by country, we determined the centroid location of each city using Google's Geocoding API.

@@

Our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities, thus we restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset. To determine proximity, we calculate the distance in kilometers between the centroid of each of the conflicts with the centroids of city locations. Meaning that for each year we determine the distance between every conflict and every major city within a state. For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of red, and the major cities therein, blue diamonds.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light red and later years shaded in dark red. Thus for every year we made six distance calculations -- one for every city.

@@

>>>>

To measure economic performance we use annual percent change in GDP collected from the World Development Indicators at the World Bank. Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average. This allows us to estimate the direct effect of conflict on economic performance in that year. A ten or five year average approach would hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.

To determine the location of conflicts we turn to the PRIO Conflict Site Dataset. This dataset contains geo-referenced armed conflict events from 1989 to 2008. In total this dataset provides us with approximately 800 geo-referenced internal conflict-year cases. To gather information on capital and major cities we turn to yearly editions of The World Almanac from 1989 to 2008. Typically, the Alamanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008.

@@

Our analysis focuses on exploring variations in economic growth in countries undergoing conflict by the proximity of those conflicts to major cities, thus we restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset. To determine proximity, we calculate the distance in kilometers between the centroid of each of the conflicts with the centroids of city locations. Meaning that for each year we determine the distance between every conflict and every major city within a state. For example, in figure \ref{fig:columbiaMap} we show the location of armed conflicts in Colombia, dots colored in shades of blue, major cities, depicted as triangles, and the capital, a diamond.\footnote{One armed conflict involving rebel actors and the Colombian government occurred outside of Colombia's borders.} For Colombia each of the red dots represents the same conflict but a different year, with earlier years shaded in light blue and later years shaded in dark blue. Thus for every year we made six distance calculations -- one for every city.

@@

A drawback with circular conflict zones is that they cover more territory than is actually affected by the conflict, including territories of neighboring countries.4 Due to the nature of armed conflict it may be impossible to gain information on the exact locations of armed encounters, occupied territories, and rebel bases. It might be possible to map the actual conflict-affected area with high precision for some well- reported conflicts, but it would be virtually impossible to code all conflict-years in the dataset coherently in a similar manner. The operationalization of conflict zones is essentially a trade-off between precision and simplicity, and in most cases a circular conflict zone will give a good indication of the core area of the conflict.
